---
title: "Internet Ad"
author: "Anisha Wadhwa"
date: "February 29, 2016"
output: html_document
---

# Capstone Data Set - EDA
####Importing Data set from text file: 

```{r}
read.csv("~/Practice Internet Ad/Ad Practice/ad-dataset (2)/ad.data", header=FALSE)
```

###Summary Stats
```{r}
summary(ad)
```

## Get the "shape" of the data
```{r}
dim(ad)
head(ad)
tail(ad)
str(ad)
```



## Importing and Assigning Variable labels (df dataset)
###Importing the names 
```{r}
install.packages("readxl")
library(readxl)
df <- read_excel("Variable name .xlsx")
```


###Transposing from column to row 

```{r}

View(t(df))

var.names <- t(df)
```


###Attaching Varible Labels to the dataset 
```{r}
colnames(ad) <- var.names 

```


## Converting variables into relevant vectors:
### Variable 1:4 from factor to numeric

```{r}
install.packages("plyr")
install.packages("dplyr")
library(plyr)
library(dplyr)


indx <- sapply(ad, is.factor)
ad[indx] <- lapply(ad[indx], function(x) as.numeric(as.character(x)))
```


##Converting integers to factors 
### variable 4:1558 from integer to factor


```{r}
indx2 <- sapply(ad, is.integer)
ad[indx2] <- lapply(ad[indx2], as.factor)
```


## Checking str(ad)
```{r}
str(ad)
```

## Convert "local" variable from numeric to factor
```{r}
as.factor(ad$`local `)
ad$`local `<- as.factor(ad$`local `)
```



##convert dependent variable into factor from numeric 
##???? NOT SURE! 

## Removing rows with NA data -- don't want to do this 
### Leaves us with 0 rows

```{r}
new_ad <- ad[rowSums(is.na(ad)) > 0,]
new_ad2 <- ad[colSums(is.na(ad)) > 0,]
```


##Find a threshold value for when to not use a specific column? 
## OR REPLACE WITH MEAN OR MODE

